Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-06-24 Tex/CAV2019/replyVSTTEJUNE2020.tex
added response
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{resposta} 
Alessandro: Provavelmente eu tenha que melhorar o texto, pois a escolha de uma solução factível ou não achar uma solução factível já é por model checking ( e isso corresponde a 1a parte da técnica), a 2a parte é uma busca linear mas com teste de SUCCESS ou FAIL para gerar contraexemplo (e, pra mim, é model checking de novo).Pra mim, estamos aplicando model checking duas vezes na técnica. \textbf{Que achas?}

@@

- Page 2: specialist PV optimization software -> specialized PV optimization software
done

@@

- page 6: Therefore, here in this study, the definition given here -> Therefore, the definition given here

@@

\begin{resposta}
Thank you, we corrected the text.
\end{resposta}

- Page 10: start-of-the-art -> state-of-the-art
done

@@

Progress has been made worldwide; in particular, in 2017, the number
of people without electricity access fell below 1 billion thresholds
-> Progress has been made worldwide; in particular, in 2017, the number
of people without electricity access fell below 1 billion

they have the drawback of an incomplete coverage ->
they have the drawback of incomplete coverage

@@

\begin{resposta}
Thank you, we corrected the the two occurrences to "not feasible".
\end{resposta}

@@

are still unexplored in literature
$->$

@@

using the traditional techniques
->

@@

For the automated synthesis
->

>>>>

\begin{resposta} 
Alessandro: Provavelmente eu tenha que melhorar o texto, pois a escolha de uma solução factível ou não achar uma solução factível já é por model checking ( e isso corresponde a 1a parte da técnica), a 2a parte é uma busca linear mas com teste de SUCCESS ou FAIL para gerar contraexemplo (e, pra mim, é model checking de novo).Pra mim, estamos aplicando model checking duas vezes na técnica. \textbf{Que achas?}  \textbf{Lucas: Concordo. Nao poderia aplicar uma busca binaria como fizemos no nosso journal do IJES?}

@@

- Page 2: specialist PV optimization software -$>$ specialized PV optimization software
done

@@

- page 6: Therefore, here in this study, the definition given here -$>$ Therefore, the definition given here

@@

\begin{resposta}
Implemented as suggested.
\end{resposta}

- Page 10: start-of-the-art -$>$ state-of-the-art
done

\begin{resposta}
Implemented as suggested.
\end{resposta}

@@

Progress has been made worldwide; in particular, in 2017, the number
of people without electricity access fell below 1 billion thresholds
-$>$ Progress has been made worldwide; in particular, in 2017, the number
of people without electricity access fell below 1 billion

\begin{resposta}
Implemented as suggested.
\end{resposta}

they have the drawback of an incomplete coverage -$>$
they have the drawback of incomplete coverage

\begin{resposta}
Implemented as suggested.
\end{resposta}

@@

\begin{resposta}
Thank you, we corrected the the two occurrences to ``not feasible''.
\end{resposta}

@@

are still unexplored in literature
-$>$

@@

using the traditional techniques
-$>$

@@

For the automated synthesis
-$>$
